Splitting It Up: The \pkg{spduration} Split-Population Duration Regression Package for Time-varying Covariates

### 2017-10-02 R Journal/beger-hill-metternich-minhas-ward.tex
add 'distr = "weib"' instead of assuming default; fixes #2

\begin{example}
  bscoup <- add_duration(bscoup, "coup", unitID = "countryid", 
  +    tID = "year", freq = "year", ongoing = FALSE)
  Warning message:
  In attempt_date(data[, tID], freq) :
  Converting to 'Date' class with yyyy-06-30
\end{example}

@@

\begin{example}
  weib_model <- spdur(
  +    duration ~ milreg + instab + regconf,
  +    atrisk ~ couprisk + wealth + milreg + rwar + regconf + samerica + 
  +      camerica,
  +    data = bscoup, silent = TRUE)

@@

\begin{example}
  weib_model2   <- spdur(
  +    duration ~ milreg + instab + regconf,
  +    atrisk ~ couprisk + wealth + milreg + rwar + regconf + samerica + 
  +      camerica,
  +    data = coup_train, silent = TRUE)

>>>>

\begin{example}
  bscoup$coup <- ifelse(bscoup$coup=="yes", 1, 0)
  bscoup <- add_duration(bscoup, "coup", unitID = "countryid", 
  +    tID = "year", freq = "year", ongoing = FALSE)
  Warning message:
  In attempt_date(data[, tID], freq) :
  Converting to 'Date' class with yyyy-06-30
\end{example}

@@

\begin{example}
  weib_model <- spdur(
  +    duration ~ milreg + instab + regconf,
  +    atrisk ~ couprisk + wealth + milreg + rwar + regconf + samerica + 
  +      camerica,
  +    data = bscoup, distr = "weib", silent = TRUE)

@@

\begin{example}
  weib_model2   <- spdur(
  +    duration ~ milreg + instab + regconf,
  +    atrisk ~ couprisk + wealth + milreg + rwar + regconf + samerica + 
  +      camerica,
  +    data = coup_train, distr = "weib", silent = TRUE)
